Titulo

### 2015-03-06 Paper/ms.tex
Organizing Everything + English Names

\cite{PartridgePeebles} predicted a population of galaxies with a strong 
Lyman Alpha (\lya) emission,  nowadays galaxies selected using the \lya 
line are known as Lyman Alpha Emitters (LAEs). Since the first 
observed LAE by \cite{DjorgovskiThompson} different teams have 
observed several LAEs \cite{Kulas12, Yamada2012,
  Chonis2013,Finkelstein2013,Ostlin14} with the aim of exploring the
extragalactic Universe.  Specially at $z>=2$ since it is when
the  line is redshifted into the optical regime. With the outcoming of
new and powerfull telescopes such as the James Webb Space Telescope
new LAEs are going to be discovered with a better resultation and at
higher redshifts.

This observations have a direct impact in studing the reionization epoch
see \cite{review} fore more details and references in within,
properties of the interstellar medium (ISM) and the intergalactic medium (IGM)
\citep{Behrens13} \citep{DijkstraKramer}, constraining star formation 
rates, understanding galaxy luminosity functions \cite{Max} and
studying the large scale structure of the Universe. In all of this
studies is required a understanding the processes 
that model the morphology and the emission of the \lya line.

To fully understand the observed spectra of the LAEs this galaxies must be
modeled. However the resonant nature of the lines makes this a challenging
task. Analytical solutions for the outcoming spectra in simple ISM static
geometries have been derived \cite{Adams72, Harrington73, Neufeld90,
  Dijkstra06}.Most recently \cite{Garavito14} have studied in
detail the effect of rotation on the lyman alpha line.
Hydrodynamical simulations have studied the
outcomming spectra of LAEs in large scale simulations, while some
others have studied detailed galaxies \citep{Verhamme12}.  
Radiative transfer codes \citep{Laursen09, Verhamme06, CLARA}have been
used in order to understand the effect of the gas kinematics in the
\lya line.

Especial attention have been devoted to model the presence of
outflows in the galaxy, motivates by previous observational 
studies . Outflows are a consecuence of the
intergalactic medium (IGM) being ejected from the galaxy due to
supernova explotions. Here different models have attempt to 
simulate more realistic situations involving shell models and cavities. 
\citep{Behrens2014}.

Despite the fact that outflows have been broadly studied 
rotation should also be present in this galaxies. T
he joint effect of the two above properties should have 
a direct effect on the morphology of the \lya line.

Study this effect is the main motivation of this paper in which we combine the
effect of rotation followed by an outflow. We proposed a simplyfied
model in which the galaxy is modeled as an sphere undergoing
solid-body rotation, with an homogeneous mixture of dust and 
hydrogen at a constant temperature.

@@

This paper is structured as follows. In \S \ref{sec:theo} we explain
in detail the model of rotation and outflow that we use as well of our
joint model (Rotation \& Outflow). In \S \ref{sec:results} we present
the results of our model. In \S \ref{sec:discussion} we compare our
results with  recent observations of LAEs with special attention of
those morphologies that present features of galaxy rotation and
outflows. In the latest section we present our  conclusions.

>>>>

\cite{PartridgePeebles} predicted a population of galaxies with a strong 
Lyman Alpha (\lya) emission,  nowadays galaxies selected using the \lya 
line are known as Lyman Alpha Emitters (LAEs). Since the first 
observed LAE by \cite{DjorgovskiThompson} different teams have 
observed several LAEs \cite{Rhoads00,Gawiser2007,Koehler2007,Ouchi08,Yamada2012,Schenker2012,Kulas12, Yamada2012, Chonis2013,Finkelstein2013,Ostlin14} 
with the aim of exploring the extragalactic Universe.  Specially at $z>=2$ since it is when
the  line is redshifted into the optical regime. With the outcoming of
new and powerful telescopes such as the James Webb Space Telescope
new LAEs are going to be discovered with a better resolution and at
higher redshifts.

This observations have a direct impact in studying the reionization epoch
see \cite{review} fore more details and references in within,
properties of the interstellar medium (ISM) and the intergalactic medium (IGM)
\citep{Behrens13} \citep{DijkstraKramer}, constraining star formation 
rates of high redshift galaxies, understanding galaxy luminosity functions \cite{Max} and
studying the large scale structure of the Universe. In all of this
studies is required an understanding of the processes 
that model the morphology and the radiate transfer process 
behind  of the \lya line.

To fully understand the observed spectra of the LAEs this galaxies must be
modeled. However the resonant nature of the line makes this a challenging
task. Analytical solutions for the outcoming spectra in simple ISM static
geometries have been derived \cite{Adams72, Harrington73, Neufeld90,
  Dijkstra06}. Radiative transfer codes \citep{DijkstraKramer, Laursen09, Verhamme06, CLARA}
have been developed in order to understand the effect of the gas kinematics in the
\lya line, special attention have been devoted to  the effects of clumpy media \citep{Hansen06} and
expanding/contracting shell/spherical geometries started to be studied
\citep{Ahn03,Verhamme06,Dijkstra06}. Recently \cite{Garavito14} have studied in
detail the effect of rotation on the lyman alpha line.
Hydrodynamic simulations have studied the
outcomming spectra of LAEs in large scale simulations \cite{Forero12},  
Recently Monte Carlo codes have been used in 
hydrodynamic simulations to study in detail individual galaxies 
\citep{Laursen09,Barnes11,Verhamme12,Yajima12}.

Especial attention have been devoted to model the presence of
outflows in the galaxy, motivates by previous observational 
studies*. Outflows are a consequence of the
interstellar medium (ISM) being ejected from the galaxy due to
supernova explosions. Here different models have attempt to 
simulate more realistic situations involving shell models and cavities. 
\citep{Behrens2014}.

Despite the fact that outflows have been broadly studied 
rotation should also be present in this galaxies. The joint 
effect of the two above properties should have 
a direct effect on the morphology of the \lya line.

Study this effect is the main motivation of this paper in which we combine the
effect of rotation followed by an outflow. We proposed a simplified
model in which the galaxy is modeled as an sphere undergoing
solid-body rotation, with an homogeneous mixture of dust and 
hydrogen at a constant temperature.

@@

This paper is structured as follows. In \S \ref{sec:theo} we explain
in detail the model of rotation and outflow that we use as well and our
joint model (Rotation \& Outflow). In \S \ref{sec:results} we present
the results of our model. In \S \ref{sec:discussion} we compare our
results with recent observations of LAEs with special attention of
those morphologies that present features of galaxy rotation and
outflows. In the latest section we present our conclusions.
